---
title: "AS03_join_edu_data"
author: "b06109022 呂紀廷"
date: "10/13/2020"
output:
  html_document:
    highlight: zenburn
    number_sections: no
    theme: cerulean
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo =TRUE)
```


```{r}
library(tidyverse)
options(stringsAsFactors = F)
```

# Q1 Joining educational data
- Reading educational data from the following csv file.

## Reading education data
```{r}
df <- read_csv("~/Desktop/呂紀廷/台灣大學/大四上/資料科學與社會研究/ver2/R4CSS-master/data/opendata107Y020.csv") %>%
    slice(-1) %>% 
    glimpse()
```


## Town level educational data 
- Original data is village-level data
- Using `group_by()` to create town-level statistical data.

```{r}
library(stringr)
tidy_df <- df  %>%
  gather("key", "value", 6:ncol(.)) %>%
  mutate(key = str_replace(key, "edu_", "")) %>%
  mutate(key = str_replace(key, "2ys_", "")) %>%
  mutate(key = str_replace(key, "5ys_final2y_", "")) %>%
  mutate(key = str_replace(key, "5ys_first3y_", "")) %>%
  mutate(key = str_replace(key, "selftaughtl_", "selftaughtl_graduated_")) %>%
  mutate(key = str_replace(key, "illiterate_", "illiterate_ungraduated_")) %>% 
  separate(key, c("degree", "graduated", "gender")) %>%
  mutate(value = as.numeric(value)) %>%
  select(-statistic_yyy) %>%
  arrange(site_id) 

tidy_df %>% head(10)
```

```{r}
town_df <- tidy_df %>% 
  mutate(site_id = str_replace(site_id, "鳳山一|鳳山二", "鳳山區"),
         site_id = str_replace(site_id, "三民一|三民二", "三民區")) %>% 
  mutate(edu_age_15up_total = as.numeric(edu_age_15up_total)) %>%
  group_by(site_id) %>%
  summarise(age_15up = sum(edu_age_15up_total),
            doctorGradSum = sum(value[graduated == "graduated" & degree == "doctor"]),
            masterGradSum = sum(value[graduated == "graduated" & degree == "master"]),
            universityGradSum = sum(value[graduated == "graduated" & degree == "university"]),
            womenSum = sum(value[gender == "f"])) %>%
  ungroup() 

town_df %>% head(10)
```


## Loading town-level age, marriage, and referendum data
- Loading previous town-level age-marriage-referendum-data
```{r}
ref10 <- read_csv("/Users/terrylu/Desktop/呂紀廷/台灣大學/大四上/資料科學與社會研究/ver2/R4CSS-master/data/referendum_byTown/ref10.csv")  %>% 
  select(county = 縣市, town = 鄉鎮市區,
         agree = 同意票數, disagree = 不同意票數,
         legalVote = 有效票數, illegalVote = 無效票數,
         vote = 投票數, legalPopulation = 投票權人數) %>% 
  mutate(site_id = str_c(county, town)) %>%
  select(site_id, agree) %>%
  drop_na(site_id)
```

```{r}
referendum <- read_csv("/Users/terrylu/Desktop/呂紀廷/台灣大學/大四上/資料科學與社會研究/ver2/R4CSS-master/town_stat.csv")%>%
  left_join(ref10, by = "site_id")
```
```{r}
referendum %>%  head(10)
```



## Joining data together
- Joining two town-leave data together 
- data 1: new added educational data
- data 2: previous age-marriage-referendum-data

```{r}
joint_df <- town_df %>% left_join(referendum, by = "site_id",
                            suffix = c("_town", "_referendum"))
joint_df %>% head(10)
```


## **Q1 Ans: Joined data dimension**
- using `dim()` to display data dimension (should be 368). 
- TAs will score Q1 according to the outcome.

```{r}
# dim(YOUR_DATA_FRAME_NAME)
dim(joint_df)
```


## **Q1 Ans: glimpse()**
- Using `glimpse()` to print out data you join below. 
- TAs will score Q1 according to the `glimpse()` outcome.

```{r}
# glimpse(YOUR_DATA_FRAME_NAME)
glimpse(joint_df)
```

# Q2 Open Question - Joining one more dimension
- TASK: Collecting one more dimension from open data and join it to the above two-level data
- e.g., economic, wealth, educational resource, ...


## Read the file
```{r}
income_tax_df <- read_csv("/Users/terrylu/Desktop/呂紀廷/台灣大學/大四上/資料科學與社會研究/ver2/R4CSS-master/data/income_tax.csv")
```

## Display the data dimension of the file
```{r}
dim(income_tax_df)
```

## Add code chunks as you need
```{r}
tidy_income_tax_df<-income_tax_df%>%
  mutate(site_id = paste(縣市,鄉鎮市區,sep = ""))%>%
  select(site_id,average_income_tax=平均數)%>%
  group_by(site_id)%>%
  summarise(average_income_tax = sum(average_income_tax)) %>% 
  ungroup()


tidy_income_tax_df %>% head(10)

```



```{r}
joint_income_tax_df <- joint_df %>% left_join(tidy_income_tax_df, by = "site_id")

joint_income_tax_df  %>% head(10)
```

## **Q2 Ans: Answer following questions**
- Data source link (the page you download the data): 
- Describe the data source in your words: 

Data source link (the page you download the data): https://data.gov.tw/dataset/103066

Describe the data source in your words: 

1, data source: government database 

2, data description: the income tax based on different areas 

3, my cleaning: I select the average income tax and join the original data.

## **Q2 Ans: Dim() of joined data frame**

```{r}
# dim(YOUR_DATA_FRAME_NAME)
dim(joint_income_tax_df )
```


## **Q2 Ans: glimpse() of joined data frame**
```{r}
# glimpse(YOUR_DATA_FRAME_NAME) 
glimpse(joint_income_tax_df) 
```

# Q3 Open question - Linear regression
 - Now, you have age, marriage, and education as indenpendent variables and referendum 10th agreement as the dependent variable.
 - Go online and search how to run regression with R
 - Report the regression result 

## **Q3 Ans**
```{r}

library(stats)
regression1 <- lm(formula = agree ~ elderSum + marriedSum + doctorGradSum + masterGradSum + universityGradSum, data = joint_income_tax_df) 


regression1
# code for print out regression result 
```
Interpreation

When the citizen is older than 65, 1-year older increases his agree rate of 10th agreement by 0.20778

1-increase of married couple raises the agree rate of 10th agreement by 0.58881

The agree rate of referendum 10th agreement by graduated voters:

doctor degree: increases 0.90128, compared to those who didn't graduate

master degree: decreases 0.57866, compared to those who didn't graduate

university degree: decreases 0.06061, compared to those who didn't graduate



# Q4 Challenge: The median of grouped data
- Calculating age median of grouped data
- Reference: https://www.themathdoctors.org/finding-the-median-of-grouped-data/
- Solve it by dplyr pkgs
- If you can't answer the question correctly, keep your code (even wrong) to get partial scores.

## **Q4 Ans: glimpse()**
```{r}
age <- read_csv("/Users/terrylu/Desktop/呂紀廷/台灣大學/大四上/資料科學與社會研究/ver2/R4CSS-master/data/opendata107Y030.csv") %>%
  slice(-1) %>% 
  mutate(vname = str_c(site_id, village)) %>%
  select(vname, everything())  # 把vname放在最前面


tidy_data <- age %>%
  gather("key", "value", 6:ncol(.)) %>%  # 第6行到最後一行做婚姻狀況、性別、年齡的交成
  mutate(key = str_replace(key, "_age", "")) %>%   # 統一key寫法（都有三個底線）
  mutate(key = str_replace(key, "100up", "100_110")) %>%
  mutate(key = str_replace(key, "15down", "0_15")) %>%
  separate(key, c("married", "ageLower", "ageUpper", "gender")) %>% 
  mutate(age = str(ageLower, ageUpper), 
         ageLower = as.numeric(ageLower),
         ageUpper = as.numeric(ageUpper),
         value = as.numeric(value)) %>%
  select(-statistic_yyy) %>%
  group_by(vname) %>% mutate(totalPopulation = sum(value),
                             cumSum = cumsum(value)) %>% 
  ungroup() %>%
  arrange(vname)

# grouped median
library(data.table)

med_data <- tidy_data %>% mutate(age = str_c(ageLower, ageUpper, sep = "-"))
setDT(med_data)
age_order <- c("0-15", "15-19", "20-24", "25-29","30-34", "35-39", "40-44",
               "45-49", "50-54", "55-59", "60-64", "65-69", "70-74", "75-79",
               "80-84", "85-89", "90-94", "95-99", "100-110")
med_data[, age := factor(age, levels = age_order)]  # variable AGE has various levels
med_data[, age_group := as.integer(age)]  # add different age group
# operator: " := "
# age := var1, meaning that add var1 to column "age"
setkey(med_data, vname, age)

library(matrixStats)

med_data[, median_group := weightedMedian(x = age_group, w = value, ties = "min"), by = vname]
med_data[, median_age := levels(age)[median_group]]

med_data<-med_data %>% group_by(vname) %>% select(vname, median_age) %>% unique() %>% arrange(vname)

glimpse(med_data)

```

