---
title: "AS4 b06109022 呂紀廷"
output: 
  html_document:
    code_folding: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
options(stringsAsFactors = F)
```



# Loading data

```{r echo=TRUE}
data_url <- "https://github.com/P4CSS/R4CSSData/raw/main/newswawawa_yt_comments.rds"
raw <- read_rds(url(data_url))
```



# 1. Data Coverage: density plot

```{r}
raw%>%glimpse()

raw %>%
    ggplot() + aes(publishedAt) + 
    geom_density()
```

# 2. Data Converage: weekly or monthly
- Hint: using `floor_date()`


```{r}
raw %>%
    mutate(m = floor_date(publishedAt , unit = "month")) %>% 
    count(m) %>%
    ggplot() + aes(m, n) + 
    geom_col()
```

# 3. Demographic
- Add more demographic features here, at least more 2 features

```{r}
message("Number of videos: ", length(unique(raw$videoId)))
message("Number of comments: ", length(unique(raw$commentId)))
message("Number of commentors: ", length(unique(raw$authorDisplayName)))
```


# 4. Number of comment distribution per video: density plot
Hint: using ggplot2 `xlab()` to label the x-axis

```{r}
raw %>%
    group_by(videoId) %>% 
    count() %>%
    ggplot() + aes(n) + 
    geom_density()+xlab('Number of comments per post')
```



# 5. Number of comments distribution
- Hint: Using `scale_y_log10()` and `scale_x_log10()` to adjust y-axis scale
- Using `geom_jitter()` to plot scatter

```{r}
raw %>%
    group_by(videoId) %>% 
    count()%>%select(videoId,numberofcomment=n)%>%
    group_by(numberofcomment)%>%
    count()%>%
    ggplot() + aes(numberofcomment,n) + 
    scale_y_log10()+scale_x_log10()+
    geom_jitter(alpha=0.4)+
    xlab('Number of comments per post')+
    ylab('Number of posts')

```


# 6. Comment patterns each month
- Filter comments after 2019-09-30, before 2020-02-01 
- density plot per month
- subplot by `facet_wrap()` with argument `scales = "free"`

```{r}
raw %>%
    filter(publishedAt > as_date("2019-09-30") & publishedAt < as_date("2020-02-01")) %>%
    mutate(m = floor_date(publishedAt, unit = "month")) %>%
    mutate(d = floor_date(publishedAt, unit = "day")) %>%
    group_by(m)%>%
    ggplot() + aes(d) + 
    geom_density()+
    facet_wrap(~as.character(m) ,scales = "free")+
    xlab('publishedAt')
```



# 7. Comments patters by week
- Filter comments after 2019-12-01, before 2020-02-01 


```{r}
raw %>%
    filter(publishedAt >= as_date("2019-12-01") & publishedAt < as_date("2020-02-01")) %>%
    mutate(w = floor_date(publishedAt, unit = "weeks")) %>%
    mutate(d = floor_date(publishedAt, unit = 'days')) %>%
    count(w,d)%>%
    ggplot() + aes(d,n) + 
    geom_col()+
    facet_wrap(~as.character(w) ,scales = 'free_x')+
    xlab('wday')
```


# 8. Comments pattern by hour per day
- Filter comments after 2019-12-30, before 2020-01-20 
- may using `ifelse()` ternary operation to divide plot into two parts: after and before 2020-01-11


```{r}
raw %>%
    filter(publishedAt >= as_date("2019-12-30") & publishedAt < as_date("2020-01-20")) %>%
    mutate(d = floor_date(publishedAt, unit = "day")) %>%
    mutate(h = hour(publishedAt)) %>%
    count(d, h) %>%
    mutate(is0111 = ifelse(d >= as_date("2020-01-11"), "after 01-11", "before")) %>%
    ggplot() + aes(h, n, color = as.character(d)) + 
    geom_line() + 
    facet_wrap(~is0111)
```

# 9. Challenge: Growth of unique member

```{r}
raw %>%
    mutate(d = floor_date(publishedAt, unit = "day")) %>%
    arrange(d)%>%
    distinct(authorDisplayName,.keep_all = T)%>%
    group_by(authorDisplayName,d)%>%
    count()%>%
    arrange(d)%>%
    ggplot() + aes(as.Date(as.character(d), '%Y-%m-%d'), cumsum(n))+ 
    geom_line()+
    xlab('publishedAt')+ylab('unique_commentor')

```

